GWAS datasets for FDR benchmarking

### 2017-09-21 datasets/GWAS/GWAS.Rmd
Increase to 100K SNPs and add directory pointers

```{r, wkspace-setup}
# Note that swfdr package depends on R version 3.4 or higher
setwd("/n/irizarryfs01_backed_up/kkorthauer/FDR")
source("benchmark-fdr/simulation_studies/R/simulation-helpers.R")
source("benchmark-fdr/datasets/R/evaluation-helpers.R")
setwd("DATA/GWAS")

@@

```{r, GWAS1-verify-contents}
bmi <- fread("BMI.SNPadjSMK.CombinedSexes.AllAncestry.txt", header=TRUE)
dim(bmi)
head(bmi)
```

@@

# Demo on a small subset of SNPs first (remove this later)
bmi <- bmi[sample(1:nrow(bmi), 10000),]
```

@@

```{r, GWAS1-run, results="hide"}
cutoffs <- c(0.01, 0.025, 0.05, 0.10, 0.20)
resfile <- paste0("bmi_results_", nrow(bmi), ".RData")
if (!file.exists(resfile)){
  bmi_results <- run_benchmarks(dat=bmi, alphas=cutoffs)
  save(bmi_results, file=resfile)
}else{
  load(resfile)
}

@@

```{r, GWAS1-cleanup}
rm(bmi)
rm(asthma_results)
```

@@

```{r, GWAS2-verify-contents}
# read in meta-data
meta <- read_xls("gabriel_results_description.xls")
head(meta)
dim(meta)

# read in data
asthma <- fread("gabriel_asthma_meta-analysis_36studies_format_repository_NEJM.txt", header=TRUE)
dim(asthma)

@@

# Demo on a small subset of SNPs first (remove this later)
asthma <- asthma[sample(1:nrow(asthma), 10000),]
```

@@

```{r, GWAS2-run, results="hide"}
# use same cutoffs as for the bmi study (defined above)
resfile <- paste0("asthma_results_", nrow(asthma), ".RData")
if (!file.exists(resfile)){
  asthma_results <- run_benchmarks(dat=asthma, alphas=cutoffs)
  save(asthma_results, file=resfile)
}else{
  load(resfile)
}

@@

```{r, GWAS3-verify-contents}
# read in data
trig <- fread("jointGwasMc_TG.txt", header=TRUE)
dim(trig)
head(trig)
```

@@

# Demo on a small subset of SNPs first (remove this later)
trig <- trig[sample(1:nrow(trig), 10000),]
```

@@

```{r, GWAS3-run, results="hide"}
# use same cutoffs as for the bmi study (defined above)
resfile <- paste0("trig_results_", nrow(trig), ".RData")
if (!file.exists(resfile)){
  trig_results <- run_benchmarks(dat=trig, alphas=cutoffs)
  save(trig_results, file=resfile)
}else{
  load(resfile)
}

>>>>

```{r, wkspace-setup}
# Note that swfdr package depends on R version 3.4 or higher
setwd("/n/irizarryfs01_backed_up/kkorthauer/FDR")
source("benchmark-fdr/simulation_studies/R/simulation-helpers.R")
source("benchmark-fdr/datasets/R/evaluation-helpers.R")
datdir <- "/n/irizarryfs01_backed_up/kkorthauer/FDR/DATA/GWAS/"
resdir <- "/n/irizarryfs01_backed_up/kkorthauer/FDR/RESULTS/GWAS/"

@@

```{r, GWAS1-verify-contents}
bmi <- fread(paste0(datdir, "BMI.SNPadjSMK.CombinedSexes.AllAncestry.txt"),
             header=TRUE)
dim(bmi)
head(bmi)
```

@@

# Demo on a small subset of SNPs first (remove this later)
bmi <- bmi[sample(1:nrow(bmi), 100000),]
```

@@

```{r, GWAS1-run, results="hide"}
cutoffs <- c(0.01, 0.025, 0.05, 0.10, 0.20)
resfile <- paste0(resdir, "bmi_results_",
                  nrow(bmi), ".RData")
if (!file.exists(resfile)){
  t1 <- proc.time()
  bmi_results <- run_benchmarks(dat=bmi, alphas=cutoffs)
  save(bmi_results, file=resfile)
  message(paste0("Took ", round((proc.time()-t1)[3],1),
                 " seconds for ", nrow(bmi), " SNPs."))
}else{
  load(resfile)
}

@@

```{r, GWAS1-cleanup}
rm(bmi)
rm(bmi_results)
```

@@

```{r, GWAS2-verify-contents}
# read in meta-data
meta <- read_xls(paste0(datdir, "gabriel_results_description.xls"))
head(meta)
dim(meta)

# read in data
asthma <- fread(paste0(datdir, 
                "gabriel_asthma_meta-analysis_36studies_format_repository_NEJM.txt"),
                header=TRUE)
dim(asthma)

@@

# Demo on a small subset of SNPs first (remove this later)
asthma <- asthma[sample(1:nrow(asthma), 100000),]
```

@@

```{r, GWAS2-run, results="hide"}
# use same cutoffs as for the bmi study (defined above)
resfile <- paste0(resdir, "asthma_results_",
                  nrow(asthma), ".RData")
if (!file.exists(resfile)){
  t1 <- proc.time()
  asthma_results <- run_benchmarks(dat=asthma, alphas=cutoffs)
  save(asthma_results, file=resfile)
  message(paste0("Took ", round((proc.time()-t1)[3],1),
                 " seconds for ", nrow(asthma), " SNPs."))
}else{
  load(resfile)
}

@@

```{r, GWAS3-verify-contents}
# read in data
trig <- fread(paste0(datdir, "jointGwasMc_TG.txt"), header=TRUE)
dim(trig)
head(trig)
```

@@

# Demo on a small subset of SNPs first (remove this later)
trig <- trig[sample(1:nrow(trig), 100000),]
```

@@

```{r, GWAS3-run, results="hide"}
# use same cutoffs as for the bmi study (defined above)
resfile <- paste0(resdir, "trig_results_",
                  nrow(trig), ".RData")
if (!file.exists(resfile)){
  t1 <- proc.time()
  trig_results <- run_benchmarks(dat=trig, alphas=cutoffs)
  save(trig_results, file=resfile)
  message(paste0("Took ", round((proc.time()-t1)[3],1),
                 " seconds for ", nrow(trig), " SNPs."))
}else{
  load(resfile)
}
